---
title: "Prediction Assignment"
author: "rafaelmenmell@gmail.com"
date: "6 de julio de 2017"
output: html_document
---

```{r library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
library(randomForest)
```

## Data downloading and preparation

In this section data is dowloaded and prepared.

```{r chunk1}
download.file(url = "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv",destfile = "train.csv")
training <- read.csv(file = "train.csv",na.strings = c("NA","#DIV/0!",""))

download.file(url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",destfile = "test.csv")
testing <- read.csv(file = "test.csv",na.strings = c("NA","#DIV/0!",""))
```

First 8 columns (X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window) are useless for modelling so ther are deleted

```{r chunk2}
training <- training[,-(1:8)]
```

Columns with all NA are deleted.

```{r chunk3}
training <- training[,colSums(is.na(training))==0]
```

## Modelling

Training data set is splitted in training.model and testing.model
```{r chunk4}
index <- createDataPartition(y=training$classe, p=0.70, list=FALSE )
training.model <- training[index,]
testing.model <- training[-index,]
training.model$classe <- factor(training.model$classe)
testing.model$classe <- factor(testing.model$classe)
model1 <- randomForest(classe ~ . , data = training.model)
cm <- confusionMatrix(testing.model$classe,predict(model1,testing.model))

#Accuracy
cm$overall[1]
```
Accuracy for this random forest model is vey high, more than 99% in testing, so it's going to be used in the 20 elements exercise
